Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-01-09 ecoop/paper.tex
Updates from Overleaf

@@

\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}

@@

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open source Java projects.

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

@@

\begin{figure*}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

@@

	public void addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

>>>>

\usepackage{chngpage}

\usepackage{courier}

@@

\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small}}{}

@@

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability. Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.

We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.

We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings. We find that the biggest influencing factor is token volume. We define token volume as the combined number of tokens in all clone instances in a clone class. The majority of duplicates with a token volume of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than two external parameters decrease maintainability.
\end{abstract}

@@

\begin{adjustwidth}{-0.8in}{-0.8in}% adjust the L and R margins by 1 inch
\begin{minipage}{\linewidth}
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
package com.sb.game;

@@

	public int addTen(int x) {
|\highlightYellow|		x = x + 10; // Addition
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
package com.sb.fruitgame;

@@

	public String concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
%\caption{Example of textually equal code fragments that differ in functionality.}
%\label{fig:type1}
%\end{figure*}
\end{minipage}
\end{adjustwidth}

\begin{lstlisting}[language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small]
for i:=maxint to 0 do 
begin 
    j:=square(root(i));
end;
\end{lstlisting}
